An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2024-09-05 article.tex
no. 8 edit

Compared to revenue, the predictive performance of the XGBoost model for operating cost was slightly better, with an $R^2$ of 0.80 (with a standard deviation of 0.10). Similar to revenue, the most important predictors of operating cost were fuel, water, area and yield (see figure \ref{fig:operating_costs_sankey}). A surprising difference was the change in relative importance of activities involving tractor passes where the use of fungicide was more important for operational costs, compared to revenue, where slashing was more important (see Figure \ref{fig:region_sankey}). The connection between spraying and operational costs is intuitive in that it utilises equipment and resources to do. However, it is surprising that although spraying is considered important, that area not harvested due to disease is not, even though this would be a direct cause. The lack of importance on disease directly could be because of a low amount disease reported in the dataset (137 vineyards). The use of spraying is also unfortunately not part of the data, and could be in response to a variety of factors such as other vineyards within the region having disease or preventative sprays. The variables that feed into these decisions are also very different with diesel having the highest relative importance to slashing, and area having the greatest relative importance to the need for fungicide.
\par
Again, Region played a determining factor overall, contributing to 334 nodes within the ensemble making it the most important variable when considering all regions together. It was surprising that electricity, slashing and spraying passes were not more prominent in operating costs due to the intrinsic nature as an agricultural expense.
\par
% . Again the surrogate model did not perform well achieving an $R^2$ of 0.0931 (with a standard deviation of 0.0197) but showed similarly to revenue an importance placed on fungicide spraying and size (see figure \ref{fig:operating_tree}).
\begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{operating_costs.png}}
  \caption{The left-hand side, A,  depicts the 10 most relative  important variables in predicting Operating Costs using XGBoost as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:operating_costs_sankey}
 \end{figure}

@@

Predictions of profit performed poorly compared to operating cost and revenue with an average $R^2$ of 0.2535 and standard deviation of 0.3126. With the large standard deviation being indicative of how unstable the models created were.

>>>>

Compared to revenue, the predictive performance of the XGBoost model for operating cost was slightly better, with an $R^2$ of 0.80 (with a standard deviation of 0.10). Similar to revenue, the most important predictors of operating cost were fuel, water, area and yield (see figure \ref{fig:operating_costs_sankey}). A surprising difference was the change in relative importance of activities involving tractor passes where the use of fungicide was more important for operational costs, compared to revenue, where slashing was more important (see Figure \ref{fig:region_sankey}). The connection between spraying and operational costs is intuitive in that it utilises equipment and resources to do. However, it is surprising that although spraying is considered important, that area not harvested due to disease is not, even though this would be a direct cause. The lack of importance on disease directly could be because of a low amount disease reported in the dataset (137 vineyards). The use of spraying is also unfortunately not part of the data, and could be in response to a variety of factors such as other vineyards within the region having disease or preventative sprays. The variables that feed into these decisions are also very different with diesel having the highest relative importance to slashing, and area having the greatest relative importance to the need for fungicide.
Again, Region played a determining factor overall, contributing to 334 nodes within the ensemble making it the most important variable when considering all regions together. It was surprising that electricity, slashing and spraying passes were not more prominent in operating costs due to the intrinsic nature as an agricultural expense. However, a consideration for a bias within the dataset may be explanatory towards to the lack of these factors contributing to expenses, with the dataset being derived from vineyards actively participating within a sustainability program.
Although region plays a strong role, it was found that factors that can be considered regionally important were not always rated high in relative importance. This was noted especially when considering oversimplified models, such as the obvious partitioning of river water as the primary source of water to identify vineyards located in the riverland (with 456 of 472 vineyards in the riverland utilising riverwater). The occurence of factors dominated by particular practices also washes out the ability to determine the effects of practices and their benefits that are widely used by this sample of vineyards. A keen example is the use of techniques such as cover crops and their prevalance within the sample, where just over 85\% (5272) of vineyards utilised some form of cover crop such as grassing and only just under 4\% (225) used only bare soil (with the remaining 552 utilising a combination). The high percentage of vineyards using this type of sustainable practice means that its effect is will not be prominent within the model, and can only show what practices would further improve those already implementing these techniques, and how they are connected to these operating costs. A strength of utilising XGBoost in this context is that, a subset of particular interest can be leveraged to focus in on the combination of factors that would contribute to the specific concieved scenario.
% . Again the surrogate model did not perform well achieving an $R^2$ of 0.0931 (with a standard deviation of 0.0197) but showed similarly to revenue an importance placed on fungicide spraying and size (see figure \ref{fig:operating_tree}).
\begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{operating_costs.png}}
  \caption{The left-hand side, A,  depicts the 10 most relative  important variables in predicting Operating Costs using XGBoost as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:operating_costs_sankey}
 \end{figure}

@@

Predictions of profit performed poorly compared to operating cost and profit with an average $R^2$ of 0.2535 and standard deviation of 0.3126. With the large standard deviation being indicative of how unstable the models created were.
